% This file is derived from "sample-sigconf.tex" of the acmart master template
% from 2018/07/16, v1.54
%
% This file should be compiled with
% "acmart.cls", "acmart.dtx", "acmart.ins", "ACM-Reference-Format.bst", v1.54
%
% See "2017 ACM Master Article Template":
% https://www.acm.org/publications/proceedings-template
%

% Do keep the \documentclass "anonymous" parameter until the review process finishes
%\documentclass[sigconf,10pt]{acmart}
\documentclass[sigconf,anonymous,10pt]{acmart}


% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[SYSTOR'20]{ACM International Systems and Storage Conference}{June 2020}{Haifa, Israel}
\acmYear{2020}
\copyrightyear{2020}

%\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Proccedings of the ACM International Systems and Storage Conference}
%\editor{John Doe}
%\editor{Jane Doe}

\begin{document}

\title{SYSTOR 2020 Concise Paper Template}

% Fill in your details. The \documentclass "anonymous" parameter keeps them hidden, remove it after the review process finishes
\author{Leave Empty foFirst1 Last1}
\affiliation{%
  \institution{Institution1}
  \city{City1}
  \state{Country1}
}
\email{email1@mail.com}

\author{First2 Last2}
\affiliation{%
  \institution{Institution2}
  \city{City2}
  \state{Country2}
}
\email{email2@mail.com}

\author{First3 Last3}
\affiliation{%
  \institution{Institution3}
  \city{City3}
  \state{Country3}
}
\email{email3@mail.com}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{F. Last1 et al.}

\begin{abstract}
This document contains instructions and formatting guidelines
for authors submitting their papers to SYSTOR 2020 and a simple usage example for an ACM compliant latex file.
\end{abstract}

%% Note: Classification and Keywords are only required for the camera-ready version

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010520.10010575.10010577</concept_id>
<concept_desc>Computer systems organization~Reliability</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010553.10010562</concept_id>
<concept_desc>Computer systems organization~Embedded systems</concept_desc>
<concept_significance>100</concept_significance>
</concept>
<concept>
<concept_id>10010583.10010588.10010592</concept_id>
<concept_desc>Hardware~External storage</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Reliability}
\ccsdesc[100]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Hardware~External storage}
\ccsdesc[300]{Hardware~Sensor applications and deployments}
\ccsdesc[300]{Hardware~Wireless integrated network sensors}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\sloppy

\section{Submission Instructions}

Submit your file electronically by \textbf{March 3, 2020 (papers)} following the instructions at \url{http://www.systor.org/2020/cfp.html}.

\subsection{Page Limits}
\begin{itemize}
	\item \textbf{Full papers} may include at most 10 pages of content using 10pt font, including everything except references.
	\item \textbf{Short papers} may include at most 5 pages of content using 10pt font, including everything except references.
\end{itemize}

\subsection{Formatting}
\begin{itemize}
	\item
	Please use the ACM latex template for your submission. The template complies with the SYSTOR typesetting guidelines. This latex file is a simple usage example.
	
	\item
	Categories and subject descriptors are required for the camera-ready version only. You can choose not to include them in your submission. ACM Computing Classification Scheme tool can be found at: https://dl.acm.org/ccs/ccs.cfm
	
	\item
	The review process is \textbf{double-blinded}. The "anonymous" parameter keeps authors' name and affiliation hidden, remove it after the review process finishes. Please refer to the sample author block in this document.
	
	\item
	Ensure that the figures and tables are legible.  Please also ensure that you refer to your figures in the main text. Many readers print the papers in gray-scale. Therefore, if you use colors for your figures, ensure that the different colors are distinguishable in gray-scale.
	
	\item
	Please note that the latest ACM format uses a separate .sty file for the copyright notice, which is used in this example. It is highly recommended you use it in your submission.
	
\end{itemize}

\subsection{Citations}

Use a \emph{number} citation format as following~\cite{lamport94,nicepaper,nicepaper2}.

\section{Camera-Ready Submission Instructions}
\begin{itemize}
	
	\item
	Do \textbf{not} include page numbers in the final manuscript.
	
	\item
	Classification and Keywords are only required for the camera-ready version (instructions in tex file).
	
	\item
	Make sure all fonts are embedded in the resulting PDF file.
	
	\item
	Authors will be individually contacted by ACM with instructions on submitting the rights management form. The system will also provide rights management text and a bibliographic strip to appear underneath the copyright notice (ISBN, doi). Authors are responsible for updating their manuscripts with this information.
	
	\item
	The finalized PDF of your paper should be submitted following the instructions at
	\url{http://www.systor.org/2020/cfp.html}.
	
	\item
	The \textbf{deadline} for submitting the final paper and ACM electronic copyright forms is 11:59pm Pacific Daylight Time (PDT) May~4, 2020.
\end{itemize}

\section*{Acknowledgments}
Acknowledgments are for the camera-ready version only. Please do not include them in your submission.

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-systor2020}
\end{document}
